---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ssrhom

<!-- badges: start -->
<!-- badges: end -->

The goal of ssrhom is to analyze data from single subject designs using hierarchical ordinal regression models.

## Installation

This process is modified for anonymization purposes.

Download the package source files from: <https://osf.io/download/eqnsp/?view_only=6866926dc56145c38b5559d51f8fc432>

Once the source files are in your working directory, you can install the package with:

```{r eval = FALSE}
install.packages("./ssrhom_0.0.3.9002.tar.gz", type = "source")
```

## Simple demonstration

Using the tasky dataset which comes with the package:

```{r}
library(ssrhom)
head(tasky)
# all arguments below are required for a given dataset
tasky_model <- ssrhom_model_ab(
  data = tasky,
  grouping = "phase", condition = "B",
  time = "time", outcome = "count", case = "person"
)
```

```{r}
# how much autocorrelation?
print(tasky_model$model, "ac")
# for a list of available effect sizes:
ssrhom_list_stats()
# non-overlap of all pairs
ssrhom_get_effect(tasky_model, stat = "nap")
# within subject standardized mean difference using pooled SD
ssrhom_get_effect(tasky_model, stat = "smd-p")
```
